Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-03 Report/conclusions.tex
Submitted version
introduction,  convergence distributed

In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by employing the \ac{SCA} technique to relax the nonconvex constraint by a sequence of convex subsets for designing the precoders to minimize the total number of user queued packets. Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} technique to address the nonconvex constraints for a fixed \ac{MMSE} receivers. We then introduced distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods. Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method. The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations. Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.

>>>>

In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using \ac{SCA} for designing the precoders to minimize the total number of user queued packets. Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers. We also proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.  The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations. Numerical results are used to compare the performance of the proposed algorithms with the existing solutions. The distributed precoder design for the time correlated fading will be considered in future.

### 2015-02-03 Report/convergence_centralized.tex
introduction,  convergence distributed

To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. Since the converged point is the minimizer for the iterative algorithm such that 
\begin{multline} \label{con-opt}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
\end{multline}
the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.

The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{multline}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

>>>>

To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. Since the converged point is the minimizer for the iterative algorithm such that 
\begin{multline} \label{con-opt}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
\end{multline}
the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions. The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.

The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO} \cite{bezdek2002some}. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{multline}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

### 2015-02-03 Report/convergence_distributed.tex
introduction,  convergence distributed

The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point. Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value. The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}. Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.

>>>>

In order to prove the convergence of the distributed algorithm, we need to prove the convergence of the decentralization approaches presented in Section \ref{sec-4}. Since the distributed algorithm outlined in Algorithm \ref{algo-3} is similar to the centralized problem, we only need to show that the distributed algorithms for the subproblem \eqref{eqn-decent-1} achieves the same solution as that of the centralized approach.

Since the subproblem defined by \eqref{eqn-decent-1} is convex, the primal decomposition approach will converge to the centralized solution if the step size diminishes as a function of the iteration index. The convergence of \ac{ADMM} scheme follows directly from the Proposition 4.2 in \cite{bertsekas1989parallel}. The overall convergence of the \ac{JSFRA} problem in a distributed approach is similar to that of the centralized convergence discussion in Appendix \ref{sec-3.5}.

Note that even if the distributed algorithms in Section \ref{sec-4} are not iterated until convergence, the objective is still monotonically decreasing following the arguments from Appendix \ref{sec-3.5}. In this case, the final solution may not reach the stationary point similar to that of the centralized solution. In the current approach, \ac{SCA} update is performed after the convergence of the distributed algorithm. It is required since the \ac{SCA} subproblems are convex and the \acl{PD} and \ac{ADMM} will converge to the centralized solution.

### 2015-02-03 Report/dual_approach.tex
introduction,  convergence distributed

In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the centralized problem \eqref{eqn-decent-1}. The \ac{ADMM} is preferred over the \ac{DD} method proposed in \cite{tolli2011decentralized} for its robustness and better convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar decomposition for the precoder design in the minimum power context is considered in \cite{admm_robust}.

Using the definitions presented in the beginning of this section, we can write the \ac{BS} \me{b} specific subproblem at the \me{\ith{i}} iteration as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n}, \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b, \eqsub \\
& \text{and } \eqref{eqn-8}, \eqsub
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality assumption at the \me{\ith{i}} iteration as
\begin{equation}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual variable vector for the next iteration is updated using the subgradient update with the step size parameter \me{\rho} as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} - \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size can be chosen as discussed in \cite{boyd2011distributed}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

>>>>

In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}. The \ac{ADMM} is preferred over the \ac{DD} method proposed in \cite{tolli2011decentralized} for its robustness and better convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar decomposition for the precoder design in the minimum power context is considered in \cite{admm_robust}.

Using the definitions presented in the beginning of this section, we can write the \ac{BS} \me{b} specific subproblem at the \me{\ith{i}} iteration as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n}, \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b,  \forall n \eqsub \\
& \text{and } \eqref{eqn-8}, \eqsub
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality assumption at the \me{\ith{i}} iteration as
\begin{equation}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

### 2015-02-03 Report/introduction.tex
introduction,  convergence distributed

\subsubsection*{Main Contributions}
In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}. Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations. Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.

>>>>

\subsubsection*{Main Contributions}
In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}. Since the problem is nonconvex due to the \ac{DC} constraints, we adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations. Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.

The proposed \ac{JSFRA} formulation provides a way to control the resource allocation across sub-channels by altering the
